Inferring probabilistic stellar rotation periods using Gaussian processes

### 2017-05-11 documents/ms.tex
adding more words about celerite to the conclusion

The main aim of this work was to develop a probabilistic rotation period
inference method.
Probabilistic periods are necessary for hierarchical Bayesian inference,
particularly when performing population analysis.
This new GP method is capable of generating a catalogue of probabilistic
rotation periods which could, for example, reveal the period distribution
(and therefore potentially the age distribution) of stars in the Milky Way.
There is still room for improvement since the uncertainty estimates are not
yet truly representative and it is still only an `effective' model, not a
physical one.
However, it is probabilistic and provides more accurate periods than
alternative methods.
We therefore argue that the GP method is the best method for rotation period
inference currently available.
The code used in this project is available at
\url{https://github.com/RuthAngus/GProtation/}.

>>>>

The main aim of this work was to develop a probabilistic rotation period
inference method.
Probabilistic periods are necessary for hierarchical Bayesian inference,
particularly when performing population analysis.
This new GP method is capable of generating a catalogue of probabilistic
rotation periods which could, for example, reveal the period distribution
(and therefore potentially the age distribution) of stars in the Milky Way.
There is still room for improvement since the uncertainty estimates are not
yet truly representative and it is still only an `effective' model, not a
physical one.
However, it is probabilistic and provides more accurate periods than
alternative methods.
{\bf Although GP inference is slow as it requires a `solve' and a matrix
determinant calculation at every step of an MCMC, a new GP solver, {\tt
celerite} \citep{Foremanmackey2017} shows promise for increasing the
computional speed of GP rotation period inference by several orders of
magnitude.
We intend to integrate {\tt celerite} into our code in the near future.}
The code used in this project is available at
\url{https://github.com/RuthAngus/GProtation/}.
